Title

### 2013-02-22 main.tex
a little reorg to start free-space space-charge section
added shapes plot
a little reorg
work on short titles for figures (continuing)
implement a \punct macro for end-of-math punctuation, this may be a bad idea, but at least it would now be searchable
began commentary on lens charge interaction

@@

\section{Free Expansion Results}

\subsection{Comparison to Other Articles}

\subsection{Trends for Initial Shapes}

@@

\section{Model Results, Predictions and Implications} \label{sec:model_results}

@@

  \begin{figure}
    \centering
    \includegraphics{inc/hardware/column.jpg}
    \caption{
      Image of the majority of the prototype UEM column at UIC.
      The main vacuum chamber is laid sideways, with the high voltage (gun) at the left and the imaging system on the right.
      The magnetic levitated turbo pump hangs below the column, a scroll pump used for backing is not pictured.
      The laser system is in the background.
      All of the above is mounted on a custom shaped active vibration-canceling optical table.
      The electronic control systems are not pictured.
    }
    \label{fig:column-pic}
  \end{figure}

>>>>

\providecommand{\punct}[1]{\ensuremath{\, \text{#1}}}

@@

  %TODO refer from here to Free expansion results

@@

\chapter{Model Results, Predictions and Implications}

\section{Free Expansion Propagation}

  \subimport{inc/model_results/shapes/}{shapes}

  \subimport{inc/model_results/spacecharge/}{spacecharge}

\section{Propagtion under External Forces}

  \subimport{inc/model_results/lens_charge/}{lens_charge}

@@

  \begin{figure}
    \centering
    \includegraphics{inc/hardware/column.jpg}
    \caption[Picture of the prototype UEM column at UIC]{
      Picture of the majority of the prototype UEM column at UIC.
      The main vacuum chamber is laid sideways, with the high voltage (gun) at the left and the imaging system on the right.
      The magnetic levitated turbo pump hangs below the column, a scroll pump used for backing is not pictured.
      The laser system is in the background.
      All of the above is mounted on a custom shaped active vibration-canceling optical table.
      The electronic control systems are not pictured.
    }
    \label{fig:column-pic}
  \end{figure}
